A search for intermediate-mass black holes mergers in the \\second LIGO--Virgo observing run with the Bayes Coherence Ratio

### 2021-07-21 main.tex
ready for submission!

\usepackage{aas_macros}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{array}
\usepackage{units}
\usepackage{xcolor} % for more colours!
\usepackage{lineno}
\usepackage{dcolumn}
\usepackage[normalem]{ulem} %% for striking out text
\usepackage{subfigure}
\usepackage[T1]{fontenc}
\usepackage[breaklinks]{hyperref}
\usepackage{xspace} 
\usepackage{bm}% bold math
\usepackage{graphicx} % Include figure files

@@

% symbols
\DeclareSymbolFont{extraup}{U}{zavm}{m}{n}
\DeclareMathSymbol{\varheart}{\mathalpha}{extraup}{86}
\DeclareMathSymbol{\vardiamond}{\mathalpha}{extraup}{87}

% Keywords
\newcommand{\bilby}{{\sc \href{https://lscsoft.docs.ligo.org/bilby/}{\texttt{Bilby}}}\xspace}
\newcommand{\bilbypipe}{{\sc \texttt{bilby\_pipe}}\xspace}
\newcommand{\dynesty}{{\sc \texttt{dynesty}}\xspace}
\newcommand{\cpnest}{{\sc cpnest}\xspace}
\newcommand{\ptemcee}{{\sc ptemcee}\xspace}
\newcommand{\gwpy}{{\sc \href{https://gwpy.github.io/}{\texttt{GWpy}}}\xspace}
\newcommand{\imrphenomp}{{\sc \texttt{IMRPhenomPv2}}\xspace}
\newcommand{\seob}{{\sc \texttt{SEOBNRv4PHM}}\xspace}
\newcommand{\nrsur}{{\sc \texttt{NRSur7dq4}}\xspace}
\newcommand{\imrxhm}{{\sc \texttt{IMRPhenomXPHM}}\xspace}
\newcommand{\gstlal}{{\sc GstLAL}\xspace}
\newcommand{\cwb}{{\sc cWB}\xspace}
\newcommand{\spiir}{{\sc SPIIR}\xspace}
\newcommand{\mbta}{{\sc MBTAOnline}\xspace}
\newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{{PyCBC}}}\xspace}
\newcommand{\GWTC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2019PhRvX...9c1040A/abstract}{{GWTC-1}}}\xspace}
\newcommand{\OGC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020ApJ...891..123N/abstract}{{2-OGC}}}\xspace}
\newcommand{\IAS}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020PhRvD.101h3030V/abstract}{{IAS}}}\xspace}

@@

% author comments
\newcommand{\avi}[1]{\textcolor{orange}{[AV: #1]}}
\newcommand{\greg}[1]{\textcolor{purple}{[Greg: #1]}}
\newcommand{\rs}[1]{\textcolor{red}{[RS: #1]}}
\newcommand{\et}[1]{\textcolor{blue}{[ET: #1]}}

@@

\begin{abstract}
The detection of an intermediate-mass black hole population ($10^2-10^6$~\msun) will provide clues to their formation environments (e.g., disks of active galactic nuclei, globular clusters) and illuminate a potential pathway to produce supermassive black holes. Ground-based gravitational-wave detectors are in principle sensitive to a subset of such mergers mergers and have been used to detect one $142^{+28}_{-16}~\msun$ intermediate-mass black hole formation event. Ground-based detector data contain numerous short duration noise transients that can mimic the gravitational-wave signals from merging intermediate-mass black holes, limiting the sensitivity of searches. Here we demonstrate a Bayesian-inspired ranking statistic to detect binary black hole mergers with a lab-frame total mass $\gtrsim55$~\msun. We use this statistic to identify candidate events with lab-frame total masses $\gtrsim55$~\msun using data from LIGO's second observing run. Our analysis does not yield evidence for new intermediate-mass black holes. However, we find support for some stellar-mass binary black holes not reported in the first LIGO--Virgo gravitational-wave transient catalog, GWTC-1.
\end{abstract}

@@

A variety of techniques have been employed to search for $10^{4} - 10^{6}~\msun$ intermediate-mass black hole (IMBH) candidates including reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations ($M_{BH}$-$\sigma$ and $M_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of gamma-ray burst light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD}). However, because IMBH have smaller gravitational spheres of influence than those of supermassive black holes, it is much more challenging to observe them with these observational techniques~\cite{Mezcua:2017:IJMPD}. Additionally, the numerous IMBH candidates discovered using these techniques are ambiguous as other sources can describe observations from the candidates (e.g., light sources orbiting clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}).

Stellar mass ($M_\text{BH} < 10^{2}~\msun$) and supermassive black holes ($M_\text{BH} > 10^{6}~\msun$) have been observed and well studied since the 1970s~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}. However, there is a deficiency of observational evidence for black holes in the intermediate-mass range $10^{2} - 10^{6}~\msun$. The discovery of an IMBH population will bridge this observational gap, probe IMBH formation environments (e.g. accretion disks of active galactic nuclei~\cite{Tagawa:2021:ApJ, Li:2021:arXiv, Samsing:2020:arXiv, Tagawa:2020:ApJ, Ishibashi:2020:A&A, Grobner:2020:A&A, Yang:2019:PhRvL, McKernan:2019:ApJL, Yang:2019:ApJ, McKernan:2018:ApJ, Bellovary:2016:ApJL, McKernan:2014:MNRAS, McKernan:2012:MNRAS}, the centers of dense stellar clusters~\cite{Banerjee:2021:MNRASa, Zevin:2021:ApJ,Mapelli:2021:arXiv,Weatherford:2021:ApJL, Bouffanais:2021:arXiv, Ballone:2021:MNRAS, Kumamoto:2021:arXiv, Banerjee:2021:MNRASb, Martinez:2020:ApJ, Romero-Shaw:2020:ApJL, Anagnostou:2020:PASA}, Population-III stars~\cite{Toubiana:2021:PhRvL, Farrell:2021:MNRAS, Safarzadeh:2020:ApJL, Liu:2020:MNRAS, Inayoshi:2017:MNRAS}), and illuminate our understanding of supermassive black hole formation~\cite{Askar:2021:MNRAS, ArcaSedda:2019:arXiv, Amaro-Seoane:2007:CQGra, Gurkan:2006:ApJL}.

Compact binary coalescences (CBCs) can provide unambiguous gravitational-wave signals for IMBH candidates e.g., the $142^{+28}_{-16}~\msun$ ($90\%$ credible intervals) remnant observed from the gravitational-wave event GW190521~\cite{Abbott:2020:PhRvL} and other candidates~\cite{ligo_imbh_search, ligo_imbh_o3, pycbc_imbh}. As a binary's total mass $\text{M}_{T}$ is associated with its gravitational-wave merger frequency, $f\sim \text{M}_{T}^{-1}$,  ground-based gravitational-wave detectors ($f\sim 10^1 - 10^3\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100~\msun < \totMlab < 400~\msun$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014, Acernese:2015:CQGra}, while space-based detectors ($f \sim 10^{-2} - 10^1\ \text{Hz}$) can study the full signals of merging systems with $10^4~\msun < \totMlab < 10^7~\msun$~\cite{ Moore_2014, Lu:2019:PhRvD}. Because of the short duration of IMBH gravitational-wave signals in ground-based detectors, data quality is critical for their detection. Gravitational-wave data is characterized by numerous non-stationary terrestrial artifacts called \textit{glitches}~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}. Like signals from IMBH mergers, most glitches last for a fraction of a second, making them difficult to distinguish from astrophysical signals. These glitches can decrease the sensitivity of searches for binary black hole mergers with $\totMlab\gtrsim55$~\msun ~\cite{pycbc_short_duration_transients}.

Although a significant fraction of the glitches can be identified by testing them for coherence amongst two or more detectors and performing matched-filtering, these methods are insufficient to identify all glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}. One method to discriminate more glitches while searching for CBCs is the Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}. The Bayesian Coherence Ratio \bcr~\cite{BCR1,BCR2} is a Bayesian odds comparing the probability that the data contains coherent signals vs. incoherent glitches. In this paper, we use the \bcr to rank O2's candidate gravitational-wave signals from $55-500~\msun$ lab-frame total mass systems. For each candidate, we calculate the probability of astrophysical origin, \pastrobcr and compare to candidate events reported by the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}.

We find that (a) events reported in \GWTC, including GW170729 (likely the most massive BBH system in \GWTC) are statistically significant $\pastrobcr>0.9$; (b) three out of the eight \IAS events and candidates have $\pastrobcr>0.5$, corroborating \IAS's detection claims for GW170304, GW170727, and GW170817A; and that (c) our ranking statistic does not identify any new IMBH, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with $\pastrobcr\sim0.5$.

@@

Bayesian inference offers an alternative means to rank the significance of candidate events by computing the odds that the data contain a transient gravitational-wave signal versus instrumental glitches~\cite{BCR1}. This method relies on accurate models for the signal and glitch morphologies~\cite{BCR1}. In principle, Bayesian odds is the optimal method for hypothesis testing~\cite{BCR2}. Much of its power comes from the Bayesian evidence, the likelihood of the data given a hypothesis. However, the evidence is not used in current matched filter searches. Here, we explore a hybrid frequentist/Bayesian ranking statistic that makes use of the Bayesian evidence. We compute the Bayesian evidence under the assumption that the data either contain a coherent gravitational-wave signal, noise, or a glitch ($Z^S, Z^N, Z^G$, defined in Appendix~\ref{sec:bayesianEvidEval}). However, instead of computing true Bayesian odds, we use the evidences as a ranking statistic. We form a bootstrapped distribution of the evidence for simulated foreground and background events in order to form a frequentist ranking statistic.

@@

Introduced by \citet{BCR1}, the Bayesian Coherence Ratio for a candidate signal in a network of $D$ detectors is given by
\begin{equation}
\label{eq:bcr}
\bcr = \frac{\hat{\pi}^S Z^S}{\prod\limits^D_{i=1} \ [\hat{\pi}^G Z^G_i + \hat{\pi}^N Z^N_i]}\  ,
\end{equation}
where $\{\hat{\pi}^S, \hat{\pi}^N, \hat{\pi}^G\}$ are estimates of the astrophysical prior-odds of obtaining a signal, noise or a glitch from a stretch of data. In the limit where the estimated prior-odds equal the astrophysical prior-odds, the \bcr becomes the optimal Bayesian odds described by \citet{BCR2}.  However, as the astrophysical prior-odds are unknown, it is invalid to use the \bcr as an odds-ratio to discriminate signals from glitches. Instead, we use the \bcr as a ranking statistic to obtain a frequentist significance of a candidate \bcr-value, \candbcr, measured against a background \bcr distribution, \bgrdbcr.

Since it is impossible to shield ground-based gravitational-wave detectors from gravitational-wave signals, the LVK empirically estimates the background by repeatedly time-shifting strain data by amounts larger than the light-travel time between the two LIGO detectors~\cite{GWTC1}. We use time-shifted data to generate \bgrdbcr. Following this, each candidate's single-event false alarm probability $p_1$ of being miss-classified as a glitch is given by
\begin{equation}
    p_1 = \frac{\text{Count of } \bgrdbcr \leq \candbcr}{\text{Count of } \bgrdbcr} \ .
\end{equation}
Moreover, as we have several candidates ($N$ candidates), each with their \candbcr, we account for them by calculating a false-alarm probability with trial factors $p_N$ given by
\begin{equation}
    \fap = 1 - (1-p_1)^N \ .
\end{equation}
Finally, we can calculate the probability of the candidate signal event occurring from  a gravitational-wave, \pastrobcr with 
\begin{equation}
\pastrobcr = 1 - \fap \ . 
\end{equation}

@@

We acquire O2 candidate signal triggers (times when the detector's data has a signal-to-noise ratio above a predetermined threshold) for \bcr analysis from \pycbc~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6}.  Some of the triggers are associated with gravitational-wave events and candidates, while others are glitches. We also acquire background and simulated triggers from \pycbc to calculate \bgrdbcr and estimate values for $\{\hat{\pi}^S,\hat{\pi}^G\}$ (see Appendix~\ref{apdx:tuning-prior-odds} for details on the estimation process). The triggers are divided into two week time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period~\cite{pycbc_og4}.

\begin{table}[t]
\caption[BBH parameters correspond to duration $<454\ \text{ms}$]{\label{tab:parameters}Trigger-selection lab-frame parameter space (parameters correspond to signals with durations $<454 \ \text{ms}$ and $q\geq0.1$).}
\centering
\begin{tabular}{lrr}
\toprule
           & Minimum & Maximum\\
\midrule
Component Mass 1 [\msun] & 31.54 & 491.68\\
Component Mass 2 [\msun] & 1.32 & 121.01\\
Total Mass [\msun] & 56.93 & 496.72\\
Chirp Mass [\msun] & 8.00 & 174.56\\
Mass Ratio & 0.1 & 0.98\\
\end{tabular}
\end{table}

For our study, we filter \pycbc triggers to include only those in the parameter ranges presented in Table~\ref{tab:parameters}. This region focuses our analysis on binary black hole mergers with total masses above $\gtrsim55 \msun$, corresponding to binary systems with signal durations $<454 \ \text{ms}$ and $q\geq0.1$. The filtering process leaves us with $60,996$ background, $5,146$ simulated, and $25$ candidate signal triggers. We also include events and candidate events reported by \GWTC and the \IAS group in our list of candidate signal triggers.  A plot of the component mass space constrained by our trigger filter is presented in Fig.~\ref{fig:templateBank}.

\begin{figure*}[!ht]
{\centering \includegraphics[width=0.75\linewidth]{images/template_bank.png}
}
% time for chunk 14
% 1176955218, Apr 23, 2017, 4:00 UTC
% 1178294418, May 08, 2017, 16:00 UTC
\caption[ BCR search space.]{Component-mass boundaries for our trigger filter and parameter estimation prior. Our search is constrained to the parameter space enclosed by the gold-colored hatches, while our prior is constrained to the slightly larger parameter space enclosed by the teal-colored hatches. The purple region labeled ``IMBH'' is the parameter space where merger remnants may be IMBHs.}\label{fig:templateBank}
\end{figure*}

@@

We use a likelihood that marginalizes over coalescence time, the phase at coalescence, and luminosity distance (Eq.~80 from~\citet{intro_to_gw_bayes}). We use identical parameter estimation priors for the glitch and signal models, reflecting our ignorance of the distribution of the population properties of signals and signal-like glitches. The complete list of the priors is in Table~\ref{tab:priors}.

@@

We analyze the O2 candidates with $\totMlab > 55~\msun$ and report candidates with $\pastrobcr\geq0.3$ in Table~\ref{tab:results}. The $\hat{\pi}^S$ and $\hat{\pi}^G$ values utilized for each time-frame are reported in Appendix~\ref{apdx:alphabeta}.

Various search pipeline \pastro are not mathematically equivalent~\cite{Galaudage:2020:PhRvD}. Moreover, \pastro is not equivalent to \pastrobcr. However, by comparing a candidate's pipeline \pastro with its \pastrobcr, we can compare how significant each pipeline deems the candidate. For comparison, in Table~\ref{tab:results} we report \pastro values from \GWTC~\cite{GWTC1}, PyCBC OGC-2~\cite{pycbc_ogc_2}, PyCBC OGC-3~\cite{pycbc_ogc_2}, PyCBC `single-search'~\cite{pycbc_single_det}, IAS~\cite{IAS1, IAS2}, and \citet{bayesian_odds}'s analyses.

>>>>

\usepackage{aas_macros}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{array}
\usepackage{units}
\usepackage[dvipsnames]{xcolor} % for more colours!
\usepackage{lineno}
\usepackage{dcolumn}
\usepackage[normalem]{ulem} %% for striking out text
\usepackage{subfigure}
\usepackage[T1]{fontenc}
% \usepackage[breaklinks]{hyperref}
\usepackage{xspace} 
\usepackage{bm}% bold math
\usepackage{graphicx} % Include figure files
\usepackage[bottom]{footmisc}
\usepackage[colorlinks,urlcolor=NavyBlue,citecolor=NavyBlue,linkcolor=NavyBlue]{hyperref}

@@

% Software
\newcommand{\code}[1]{{\texttt{#1}}\xspace}
\newcommand{\bilby}{\code{bilby}}
\newcommand{\bilbypipe}{\code{bilby-pipe}}
\newcommand{\dynesty}{\code{dynesty}}
\newcommand{\gwpy}{\code{GWpy}}

% Keywords
\newcommand{\imrphenomp}{{\sc \texttt{IMRPhenomPv2}}\xspace}
\newcommand{\seob}{{\sc \texttt{SEOBNRv4PHM}}\xspace}
\newcommand{\nrsur}{{\sc \texttt{NRSur7dq4}}\xspace}
\newcommand{\imrxhm}{{\sc \texttt{IMRPhenomXPHM}}\xspace}
\newcommand{\gstlal}{{\sc GstLAL}\xspace}
\newcommand{\cwb}{{\sc cWB}\xspace}
\newcommand{\spiir}{{\sc SPIIR}\xspace}
\newcommand{\mbta}{{\sc MBTAOnline}\xspace}

% \newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{{PyCBC}}}\xspace}
% \newcommand{\GWTC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2019PhRvX...9c1040A/abstract}{{GWTC-1}}}\xspace}
% \newcommand{\OGC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020ApJ...891..123N/abstract}{{2-OGC}}}\xspace}
% \newcommand{\IAS}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020PhRvD.101h3030V/abstract}{{IAS}}}\xspace}

\newcommand{\pycbc}{{\sc {{PyCBC}}}\xspace}
\newcommand{\GWTC}{{\sc {{GWTC-1}}}\xspace}
\newcommand{\OGC}{{\sc {{2-OGC}}}\xspace}
\newcommand{\IAS}{{\sc {{IAS}}}\xspace}

@@

@@

\begin{abstract}
The detection of an intermediate-mass black hole population ($10^2-10^6$~\msun) will provide clues to their formation environments (e.g., disks of active galactic nuclei, globular clusters) and illuminate a potential pathway to produce supermassive black holes. Ground-based gravitational-wave detectors are sensitive to a subset of such mergers and have been used to detect one $142^{+28}_{-16}~\msun$ intermediate-mass black hole formation event. However, ground-based detector data contain numerous incoherent short duration noise transients that can mimic the gravitational-wave signals from merging intermediate-mass black holes, limiting the sensitivity of searches. Here we search for binary black hole mergers using a Bayesian-inspired ranking statistic which measures the coherence or incoherence of triggers in multiple-detector data. We use this statistic to identify candidate events with lab-frame total masses $\gtrsim55$~\msun using data from LIGO's second observing run. Our analysis does not yield evidence for new intermediate-mass black holes. However, we find support for some stellar-mass binary black holes not reported in the first LIGO--Virgo gravitational-wave transient catalog, GWTC-1.
\end{abstract}

@@

A variety of techniques have been employed to search for ${10^{4} - 10^{6}~\msun}$ intermediate-mass black hole (IMBH) candidates including reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations ($M_{BH}$-$\sigma$ and $M_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of gamma-ray burst light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD}). However, because IMBH have smaller gravitational spheres of influence than those of supermassive black holes, it is much more challenging to observe them with these observational techniques~\cite{Mezcua:2017:IJMPD}. Additionally, the numerous IMBH candidates discovered using these techniques are ambiguous as other sources can describe observations from the candidates (e.g., light sources orbiting clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}).

Stellar mass (${M_\text{BH} < 10^{2}~\msun}$) and supermassive black holes (${M_\text{BH} > 10^{6}~\msun}$) have been observed and well studied since the 1970s~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}. However, there is a deficiency of observational evidence for black holes in the intermediate-mass range ${10^{2} - 10^{6}~\msun}$. The discovery of an IMBH population will bridge this observational gap, probe IMBH formation environments (e.g. accretion disks of active galactic nuclei~\cite{Tagawa:2021:ApJ, Li:2021:arXiv, Samsing:2020:arXiv, Tagawa:2020:ApJ, Ishibashi:2020:A&A, Grobner:2020:A&A, Yang:2019:PhRvL, McKernan:2019:ApJL, Yang:2019:ApJ, McKernan:2018:ApJ, Bellovary:2016:ApJL, McKernan:2014:MNRAS, McKernan:2012:MNRAS}, the centers of dense stellar clusters~\cite{Banerjee:2021:MNRASa, Zevin:2021:ApJ,Mapelli:2021:arXiv,Weatherford:2021:ApJL, Bouffanais:2021:arXiv, Ballone:2021:MNRAS, Kumamoto:2021:arXiv, Banerjee:2021:MNRASb, Martinez:2020:ApJ, Romero-Shaw:2020:ApJL, Anagnostou:2020:PASA}, Population-III stars~\cite{Toubiana:2021:PhRvL, Farrell:2021:MNRAS, Safarzadeh:2020:ApJL, Liu:2020:MNRAS, Inayoshi:2017:MNRAS}), and illuminate our understanding of supermassive black hole formation~\cite{Askar:2021:MNRAS, ArcaSedda:2019:arXiv, Amaro-Seoane:2007:CQGra, Gurkan:2006:ApJL}.

Compact binary coalescences (CBCs) can provide unambiguous gravitational-wave signals for IMBH candidates e.g., the ${142^{+28}_{-16}~\msun}$ ($90\%$ credible intervals) remnant observed from the gravitational-wave event GW190521~\cite{Abbott:2020:PhRvL} and other candidates~\cite{ligo_imbh_search, ligo_imbh_o3, pycbc_imbh}. As a binary's total mass $M_{T}$ is associated with its gravitational-wave merger frequency, $f\sim M_{T}^{-1}$,  ground-based gravitational-wave detectors (${f\sim 10^1 - 10^3\ \text{Hz}}$) are sensitive to the last milliseconds of merging systems with ${100~\msun < \totMlab < 400~\msun}$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014, Acernese:2015:CQGra}, while space-based detectors (${f \sim 10^{-2} - 10^1\ \text{Hz}}$) can study the full signals of merging systems with ${10^4~\msun < \totMlab < 10^7~\msun}$~\cite{ Moore_2014, Lu:2019:PhRvD}. Because of the short duration of IMBH gravitational-wave signals in ground-based detectors, data quality is critical for their detection. Gravitational-wave data is characterized by numerous non-stationary terrestrial artifacts called \textit{glitches}~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}. Like signals from IMBH mergers, most glitches last for a fraction of a second, making them difficult to distinguish from astrophysical signals. These glitches can decrease the sensitivity of searches for binary black hole mergers with $\totMlab\gtrsim55$~\msun ~\cite{pycbc_short_duration_transients}.

Although a significant fraction of the glitches can be identified by testing them for coherence amongst two or more detectors and performing matched-filtering, these methods are insufficient to identify all glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}. One method to discriminate more glitches while searching for CBCs is the Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}. The Bayesian Coherence Ratio \bcr~\cite{BCR1,BCR2} is a Bayesian odds comparing the probability that the data contains coherent signals vs. incoherent glitches. In this paper, we use the \bcr to rank coincident CBC candidates in Hanford and Livingston O2 data with lab-frame total masses in the range of $55-500~\msun$. We present the candidates' \pastrobcr, the probability that the candidate originates from a coherent gravitational-wave source. Additionally, for comparison, we provide the candidate's \pastro values reported by  the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, and by \citet{bayesian_odds}.

We find that (a) events reported in \GWTC, including GW170729 (likely the most massive BBH system in \GWTC) are statistically significant ${\pastrobcr>0.9}$; (b) three out of the eight \IAS events and candidates have ${\pastrobcr>0.9}$, corroborating \IAS's detection claims for GW170304, GW170727, and GW170817A; and that (c) our ranking statistic does not identify any new IMBH, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222\footnote{170222 is a sub-threshold candidate detected by \pycbc (${\tc = 1171814476.97}$) with a ${\pastrobcr\sim0.6}$. The prefix of GW is not utilized as this is a candidate event.} with ${\pastrobcr\sim0.6}$.

@@

Bayesian inference offers an alternative means to rank the significance of candidate events by computing the odds that the data contain a transient gravitational-wave signal versus instrumental glitches~\cite{BCR1}. This method relies on accurate models for the signal and glitch morphologies~\cite{BCR1}. In principle, Bayesian odds is the optimal method for hypothesis testing~\cite{BCR2}. Much of its power comes from the Bayesian evidence, the likelihood of the data given a hypothesis. However, the evidence is not used in current matched filter searches. Here, we explore a hybrid frequentist/Bayesian ranking statistic that makes use of the Bayesian evidence. We compute the Bayesian evidence under the assumption that the data either contain a coherent gravitational-wave signal, noise, or a glitch ($Z^S, Z^N, Z^G$, defined in Appendix~\ref{sec:bayesianEvidEval}). However, instead of computing true Bayesian odds, we use the evidences as a ranking statistic. We form a bootstrapped distribution of the evidence for simulated foreground and background events to form a frequentist ranking statistic.

@@

Introduced by \citet{BCR1}, the Bayesian Coherence Ratio for a candidate signal in a network of $D$ detectors is given by
\begin{equation}
\label{eq:bcr}
\bcr = \frac{\hat{\pi}^S Z^S}{\prod\limits^D_{i=1} \ [\hat{\pi}^G_i Z^G_i + \hat{\pi}^N_i Z^N_i]}\  ,
\end{equation}
where $\{\hat{\pi}^S, \hat{\pi}^N_i, \hat{\pi}^G_i\}$ are estimates of the astrophysical prior-odds that the data contain a coherent signal, incoherent noise or an incoherent glitch. We assume each detector has the same glitch and noise prior odds of $\{\hat{\pi}^N, \hat{\pi}^G\}$. In the limit where the estimated prior-odds equal the astrophysical prior-odds, the \bcr becomes the optimal Bayesian odds described by \citet{BCR2}.  However, as the astrophysical prior-odds are unknown, it is invalid to use the \bcr as an odds-ratio to discriminate signals from glitches. Instead, we use the \bcr as a ranking statistic to obtain a frequentist significance of a candidate \bcr-value, \candbcr, measured against a background \bcr distribution, \bgrdbcr.

%  $\hat{\pi}^S$ is the prior odds of detector-data containing a coherent astrophysical signal versus an incoherent instrumental-artifact (such as a glitch or noise), while $\{\hat{\pi}^N_i, \hat{\pi}^G_i\}$ are prior odds of detector-data containing a glitch or noise given an incoherent instrumental-artifact is present in the data.

Since it is impossible to shield ground-based gravitational-wave detectors from gravitational-wave signals, the LVK empirically estimates the background by repeatedly time-shifting strain data by amounts larger than the light-travel time between the two LIGO detectors~\cite{GWTC1}. We use time-shifted data to generate \bgrdbcr. Following this, each candidate's single-event false alarm probability $p_1$ of being miss-classified as a glitch is given by
\begin{equation}
    p_1 = \frac{\text{Count of } \bgrdbcr \leq \candbcr}{\text{Count of } \bgrdbcr} \ .
\end{equation}
Moreover, as we have several candidates ($N$ candidates), each with a \candbcr, we account for them by calculating a false-alarm probability with trial factors $p_N$ given by
\begin{equation}
    \fap = 1 - (1-p_1)^N \ .
\end{equation}
Finally, we can calculate the probability of the candidate signal event occurring from  a gravitational-wave, \pastrobcr with 
\begin{equation}
\pastrobcr = 1 - \fap \ . 
\end{equation}

@@

We acquire candidate signal triggers (times when the detector's data has a signal-to-noise ratio above a predetermined threshold) for \bcr analysis from \pycbc's search in O2~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, public_ligo_o2_triggers}.  Some of the triggers are associated with gravitational-wave events and candidates while others are glitches. We also acquire background and simulated triggers from \pycbc's O2 search to calculate \bgrdbcr and estimate values for $\{\hat{\pi}^S,\hat{\pi}^G\}$ (see Appendix~\ref{apdx:tuning-prior-odds} for details on the estimation process). The triggers are divided into two week time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period~\cite{pycbc_og4}.

\begin{table}[t]
\caption[BBH parameters correspond to duration $\leq454\ \text{ms}$]{\label{tab:parameters}Trigger-selection lab-frame parameter space (parameters correspond to signals with durations $\leq454 \ \text{ms}$ and $q\geq0.1$).}
\centering
\begin{tabular}{lrr}
\toprule
           & Minimum & Maximum\\
\midrule
Component Mass 1 [\msun] & 31.54 & 491.68\\
Component Mass 2 [\msun] & 1.32 & 121.01\\
Total Mass [\msun] & 56.93 & 496.72\\
Chirp Mass [\msun] & 8.00 & 174.56\\
Mass Ratio & 0.1 & 0.98\\
\end{tabular}
\end{table}

For our study, we filter \pycbc triggers to include only those in the parameter ranges presented in Table~\ref{tab:parameters}. This region focuses our analysis on binary black hole mergers with lab-frame total masses above ${\gtrsim55 \msun}$, corresponding to binary systems with signal durations $<454 \ \text{ms}$ and ${q\geq0.1}$. The filtering process leaves us with $60,996$ background, $5,146$ simulated, and $25$ candidate signal triggers. We additionally include events and candidate events reported by \GWTC and the \IAS group in our list of candidate signal triggers.  A plot of the lab-fame component mass space constrained by our search space is presented in Fig.~\ref{fig:templateBank}.

\begin{figure*}[!ht]
{\centering \includegraphics[width=0.75\linewidth]{images/template_bank.png}
}
% time for chunk 14
% 1176955218, Apr 23, 2017, 4:00 UTC
% 1178294418, May 08, 2017, 16:00 UTC
\caption[ BCR search space.]{Lab-frame component-mass boundaries for our search space and parameter estimation prior. Our search is constrained to the parameter space enclosed by the gold-colored hatches, while our prior is constrained to the slightly larger parameter space enclosed by the teal-colored hatches. The purple region labeled ``IMBH'' is the parameter space where merger remnants may be IMBHs.}\label{fig:templateBank}
\end{figure*}

@@

We use a likelihood that marginalizes over coalescence time, the phase at coalescence, and luminosity distance (Eq.~80 from~\citet{intro_to_gw_bayes}). We use identical parameter estimation priors for the glitch and signal models. We restrict the spin priors to aligned spins to reduce the number of parameters we sample. We define our mass priors to be uniform in chirp mass $\mathcal{M}$ and mass ratio $q$ to avoid sampling issues that arise from sampling in thin regions of the component mass parameter space~\cite{bilby_gwtc}. As a post-processing step, we convert posterior samples calculated with uniform $\{\mathcal{M}, q\}$ priors to uniform component mass priors by re-sampling the posterior samples using the Jacobian given in Eq.~21 of \citet{Veitch:2015:PhRvD}. The complete list of the priors is in Table~\ref{tab:priors}.

@@

We analyze the O2 candidates with ${\totMlab > 55~\msun}$ and report candidates with ${\pastrobcr\geq0.2}$ in Table~\ref{tab:results}. The $\hat{\pi}^S$ and $\hat{\pi}^G$ values utilized for each time-frame are reported in Appendix~\ref{apdx:alphabeta}. By imposing a \pastrobcr threshold of 0.5, we present 13 candidate gravitational wave events.
